---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
setwd("C:/Users/Mark/Desktop/Kaggle/rpdata/RepData_PeerAssessment1")
data = read.csv("activity.csv")
data$date <- as.Date(data$date)
```

## What is mean total number of steps taken per day?

1. Get total number of steps for every day, ignoring NAs.
```{r}
total = aggregate(steps~date,data,sum)
```
2. Get mean and median total number of steps taken per day:
```{r}
meanTotal = mean(total$steps)
medianTotal = median(total$steps)
```

3. Histogram of total number of steps per day
```{r}
library(ggplot2)
g = ggplot(total,aes(steps))+geom_histogram()
print(g)
```



## What is the average daily activity pattern?
1. Time Series plot over intervals
```{r}
print(ggplot(data,aes(interval,steps)) + geom_line())
```

2. Time Series average steps plot over daily 

```{r}
meanDaily = aggregate(steps~date,data,mean)
print(ggplot(meanDaily,aes(date,steps)) + geom_line())
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
