---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
setwd("C:/Users/ub55123/Desktop/Kaggle/repdata")
data = read.csv("activity.csv")
data$date <- as.Date(data$date)
```

## What is mean total number of steps taken per day?
# get total number of steps for every day, ignoring NAs.
```{r}
total = aggregate(steps~date,data,sum)
```
#get mean and median total number of steps taken per day:
```{r}
meanTotal = mean(total$steps)
medianTotal = median(total$steps)
```
# histogram of total number of steps per day
```{r}
ggplot(total,aes(steps))+geom_histogram()
```



## What is the average daily activity pattern?
# Time Series plot over intervals
ggplot(data,aes(interval,steps)) + geom_line()
# Time Series average steps plot over daily 
meanDaily = aggregate(steps~date,data,mean)
ggplot(meanDaily,aes(date,steps)) + geom_line()


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
